\chapter*{List of Publications}
\addcontentsline{toc}{chapter}{List of Publications}
\setheader{List of Publications}
\label{publications}

%% We use the 'etaremune' environment (the reverse of 'enumerate') to get a
%% numbered list of publications in reverse chronological order. If the list of
%% authors is long, it might be useful to emphasize your own name with \textbf.
\begin{etaremune}{\small

\item {\textrm{Mountakis, K.S.}, Klos, T. and Witteveen, C. Stochastic Task Networks. In \emph{International Conference on AI and OR Techniques in Constraint Programming for Combinatorial Optimization Problems (CPAIOR)} (pp. 302--311), 2017, Springer, Cham.}

\item {\textrm{Mountakis, K.S.}, Klos, T. and Witteveen, C. Dynamic Temporal Decoupling. In \emph{International Conference on AI and OR Techniques in Constraint Programming for Combinatorial Optimization Problems (CPAIOR)} (pp. 328--343), 2017, Springer, Cham.}

\item {\textrm{Mountakis, S.}, Klos, T. and Witteveen, C. Temporal Flexibility Revisited: Maximizing Flexibility by Computing Bipartite Matchings. In \emph{International Conference on Automated Planning and Scheduling (ICAPS)}, (pp. 174--178), 2015.}

\item {\textrm{Mountakis, K.S.}, Klos, T., Witteveen, C. and B. Huisman. Exact and heuristic methods for trading-off makespan and stability in stochastic project scheduling. 
	In \emph{Multidisciplinary International Scheduling Conference: Theory and Applications (MISTA)}, (pp. 25--41), 2015.}

\item {\textrm{Mountakis, K.S.} Stochastic Scheduling of Train Maintenance Projects. Master's thesis, Delft University of Technology, The Netherlands, 2013.}

}\end{etaremune}

