This paper addresses a problem of practical value in project scheduling:
trading expected makespan for stability,
under stochastic activity duration uncertainty.
We present the formal statement of a problem 
that we name Proactive Stochastic RCPSP (PS-RCPSP).
Assuming activity durations follow known probability distributions,
PS-RCPSP asks to find a so-called earliest-start (es) policy and
a proactive schedule that together minimize the weighted 
sum of expected project makespan and expected instability
(deviation of the realized from the proactive schedule).
%
Extending an existing MILP model for the well-known deterministic 
Resource-Constrained Project Scheduling Problem (RCPSP),
we present a MILP model for PS-RCPSP, which allows us to 
find optimal (es-policy, proactive schedule) pairs.
To deal with instances of practical size,
we propose a Linear Programming (LP)-based 
and a Mixed-Integer LP (MILP)-based heuristic.
Our LP-based heuristic optimizes the proactive schedule while 
keeping the es-policy part of the solution fixed.
Our MILP-based heuristic aims to optimize the structure of the policy together with the proactive schedule.
In contrast to existing state-of-art approaches such as
CCP \cite{lamas2014purely} and STC \cite{van2008},
our heuristics rely on optimizing the proactive schedule together with the scheduling policy.
%
Experiments show that the LP-based heuristic is efficient and compares favorably with the state-of-art 
(i.e.\ achieves smaller expected makespan for a certain level of expected instability)
when the aim is to achieve near-zero instability at the cost of higher makespan.
The MILP-based heuristic seems more effective (albeit not as efficient) when the aim is to
achieve low expected makespan at the cost of moderate or high instability.
