\documentclass[print,nativefonts]{dissertation}

\input{../packages-commands}

\begin{document}

%% Specify the title and author of the thesis. This information will be used on
%% the title page (in title/title.tex) and in the metadata of the final PDF.
\title[]{{Scheduling Under Uncertainty: Attaining Flexibility, Robustness and Stability}}
\author{Kiriakos Simon}{Mountakis}

%% Use Roman numerals for the page numbers of the title pages and table of
%% contents.
\frontmatter

\include{title/title}

%% The (optional) dedication can be used to thank someone or display a
%% significant quotation.
\dedication{\epigraph{In loving memory of my father, Georgios Mountakis}{}}

\tableofcontents

\include{summary/summary}
\include{preface/preface}

%% Use Arabic numerals for the page numbers of the chapters.
\mainmatter

%% Turn on thumb indices.
%\thumbtrue

\chapter{Introduction}
\label{chapter:introduction}
\input{chapter/introduction/body}

\part{Simple Temporal Problems}
\chapter{Preliminaries}
\label{chapter/prelim-1}
\input{chapter/prelim-1/body}

\chapter[Temporal decoupling]{Temporal decoupling\protect\footnotemark{}\protect\footnotetext{
This chapter has been published as:
S. Mountakis, T.B. Klos, and C. Witteveen. Temporal flexibility revisited: Maximizing flexibility by computing bipartite matchings. 
In \emph{International Conference on Automated Planning and Scheduling (ICAPS)}, pages 174-178, 2015.}}

\label{chapter/icaps-flexibility}
\input{chapter/icaps-flexibility/body}

\chapter[Dynamic temporal decoupling]{Dynamic temporal decoupling\protect\footnotemark{}\protect\footnotetext{
This chapter has been published as:
K.S. Mountakis, T.B. Klos and C. Witteveen.  Dynamic Temporal Decoupling. 
In \emph{International Conference on AI and OR Techniques in Constraint Programming for Combinatorial Optimization Problems (CPAIOR)}, pages 328-343, 2017.}}
\label{chapter/cpaior-decoupling}
\input{chapter/cpaior-decoupling/body}

\part{Stochastic Task Networks}
\chapter{Preliminaries}
\label{chapter/prelim-2}
\input{chapter/prelim-2/body}

\chapter[Stable dispatching with resource constraints]{Stable dispatching with resource constraints\protect\footnotemark{}\protect\footnotetext{
This chapter has been published as:
K.S. Mountakis, T.B. Klos, C. Witteveen, and B. Huisman. Exact and heuristic methods for trading-off makespan and stability in stochastic project scheduling. 
In \emph{Multidisciplinary International Scheduling Conference: Theory and Application (MISTA)}, pages 25-41, 2015.}}

\label{chapter/mista-stability}
\input{chapter/mista-stability/body}

\chapter[Stable dispatching via dynamic programming]{Stable dispatching via dynamic programming\protect\footnotemark{}\protect\footnotetext{
This chapter has been published as:
K.S. Mountakis, T.B. Klos and C. Witteveen. Stochastic Task Networks: Trading Performance for Stability. 
In \emph{International Conference on AI and OR Techniques in Constraint Programming for Combinatorial Optimization Problems (CPAIOR)}, pages 302-311, 2017.}}
\label{chapter/cpaior-stability}
\input{chapter/cpaior-stability/body}

\part{Epilogue}

\chapter{Conclusion}
\label{chapter/conclusion}
\input{chapter/conclusion/body}

%\include{epilogue/epilogue}
%\include{acks/acks}

%% Use letters for the chapter numbers of the appendices.
\appendix

%\include{appendix-a/appendix-a}

%% Turn off thumb indices for unnumbered chapters.
\thumbfalse

%\include{cv/cv}
\include{publications/publications}

\bibliographystyle{mystyle}
\bibliography{dissertation}

\end{document}

